InteroceptionStudy_GPValidation

### 2021-08-21 Experiment 2.Rmd
Update Experiment 2.Rmd
quest

# self reports

@@

>>>>

# self reports
- New Tas is already scored
- score AQ, etc using https://xavierrg.shinyapps.io/datacleaning

gorilla codes

STAI:: 5nzr
AQ:7uqw
STAIS: 8rfo
Demog: 8zto
BVAQ: 83b1
BPQ: bbc4
DASS: chif
IQ: esh8
IAS: jvi8
TAS:pdlt
demog_meantal health: v2gn

consent: 8nsp

@@

Ledalab('/Users/heliocuve/Documents/InteroStudy/EATProcesing/EAT/forLeda/', 'open','biopac','downsample', 15, 'smooth',{'adapt'}, 'analyze','CDA', 'optimize',3, 'export_era', [1 6 .01 2])
